---
title: "Scopus publications and authors historigrams"
output: html_notebook
---

These plots show the distribuition of downloaded data from Scopus. Focus was on 2007 - 2017 period and authors from UE countries. From all subject areas (PHYSics, SOCIal science and MEDIcine)


### Papers

Read data and convert year column to R integers because Python saves number with .0 suffix and I still didn't found how fix this.

Then order rows by year

```{r}
pubs = read.csv2('./publications_histogram.csv', header = TRUE, sep = ',')
pubs$year = strtoi(sub("\\.0", "", pubs$year))
pubs = pubs[order(pubs$year),]
```
  
And plot years historigram
```{r}
par(las=1)
barplot(pubs$total, names.arg = pubs$year)
```

Make it a little more readable

```{r}
par(las=1)
pubs = pubs[pubs$year > 1999,]
barplot(pubs$total, names.arg = pubs$year)
```

### Authors

Read countries and order them by total number

```{r}
auths = read.csv2('./authors_country_histogram.csv', header = TRUE, sep = ',')
auths = auths[order(auths$total, decreasing = TRUE),]
```

And plot countries
```{r}
par(las=1)
barplot(auths$total, names.arg = auths$country)
```

Make it more interesting, we don't want to see Belize and Manilla physicists.

And exclude missing authors.
```{r}
par(las=1, mar=c(3,7.5,2,2))
auths$country[auths$country == ''] = NA
auths = na.omit(auths)
auths = auths[auths$total > 39000,]
barplot(auths$total, names.arg = auths$country, horiz = TRUE)
```
